\documentclass{muratcan_cv}
\usepackage{multicol}

\setname{Debakar Roy}{}
\setmobile{+91 8391887283}
\setmail{debakar.roy@outlook.com}
\setlinkedinaccount{https://www.linkedin.com/in/debakar-roy/} 
\setgithubaccount{https://github.com/debakarr} 
\setwebsite{https://debakarr.github.io/} 
\setthemecolor{MidnightBlue}

    
\begin{document}

%Create header
\headerview
\vspace{1ex} % white space
%
\section{Experience}
%
\datedexperience{Intel Corporation}{August 2022 - Present}
\explanation{Infrastructure and DevOps - SDE II / Tech Lead}{Karnataka, IN}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
        Architected and maintained test automation frameworks, resulting in \$1M savings by prioritizing critical bugs and enabling off-hours runs, boosting efficiency.
        
        \smallskip 
        \coloredbullet\ %
        Engineered scalable microservices solutions with RESTful APIs, optimizing execution across 1000+ systems, significantly improving scalability and utilization.
        
        \smallskip
        \coloredbullet\ %
        Standardized CI/CD pipelines across the organization using Jenkins shared libraries and agent templates, reducing new project setup time to 5 minutes and fostering rapid development cycles.
        
        \smallskip
        \coloredbullet\ %
        Led AI productivity initiatives, applying AI in code generation, documentation, and more, boosting productivity by 30\%.
        
        \smallskip
        \coloredbullet\ %
        Delivered Python training to 1200+ employees, saving \$1.2M and promoting continuous learning.
        
        \smallskip
        \coloredbullet\ %
        Tech lead for 4+ annual projects, guiding 20+ engineers towards technical excellence and goal alignment.
	
	\smallskip
}
%
\datedexperience{Intel Corporation}{August 2019 - August 2022}
\explanation{Software Engineer}{Karnataka, IN}
\explanationdetail{
	\coloredbullet\ %
        Pioneered test content automation across 6+ domains, including AI and Power Management, for Windows Functional Validation, automating over 1200 test cases, which constituted 15\% of the manual test plan.
        
        \smallskip 
        \coloredbullet\ %
        Was instrumental in overseeing a distributed codebase with contributions from 50+ developers, ensuring high code quality and consistency.
        
        \smallskip
        \coloredbullet\ %
        Established an efficient CI/CD pipeline with industry-standard DevOps tools, reducing deployment times by 20\%, increasing deployment frequency by 3x, and enhancing development efficiency across 4+ projects.
        
        \smallskip
        \coloredbullet\ %
        Led a 30-member development team's technical ramp-up, creating 40+ documentation guides, which cut project onboarding time by 50\% and boosted knowledge sharing efficiency by 40\%.
	     
	\smallskip
}
%
\datedexperience{Intel Corporation}{July 2018 - August 2019} 
\explanation{Undergrade Intern Technical}{Karnataka, IN} 
\explanationdetail{ 
	\smallskip 
	\coloredbullet\ %
	Developed a Python-based automation framework for RF performance and compliance automation.
	     
	\smallskip
	\coloredbullet\ %
	Leveraged Git, Intel XMM modems, Python, PyCharm IDE, CMW, and Anritsu Wideband Radio Communication Tester.
	     
	%  \smallskip
	\bigskip
} 
%
\section{Education} 
\datedexperience{Bachelor of Technology, Computer Science}{August 2015 - July 2019}
\explanation{Siliguri Institute of Technology, 9.12 DGPA}{West Bengal, IN} 
% Skills
\section{Skills}
%
\newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Python \ \ \textbf{\emph{Familiar:}} \ \  Rust \cpshalf Bash \cpshalf C++ \cpshalf JavaScript}}
%
\newcommand{\skilltwo}{\createskill{Software Development}{Programming Paradigms \cpshalf Design Patterns \cpshalf Agile methodologies \cpshalf Git \cpshalf REST \cpshalf CLI \cpshalf CI/CD}}
%
\newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{FastAPI \cpshalf Flask \cpshalf Vue \cpshalf Pandas \cpshalf Selenium \cpshalf Playwright \cpshalf Poetry \cpshalf HUGO}}
%
\newcommand{\skillfour}{\createskill{DevOps}{Jenkins \cpshalf Kubernetes \cpshalf Docker \cpshalf CloudFoundry \cpshalf Rancher \cpshalf Terraform}}
%
\newcommand{\skillfive}{\createskill{Database Technologies}{\textbf{\emph{Experienced:}} \ \ MongoDB \cpshalf Redis}}
%
\newcommand{\skillsix}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Hindi \ \ \textbf{\emph{Fluent:}} \ \ English \ \ \textbf{\emph{Beginner:}} \ \  Japanese \cpshalf Korean \cpshalf Mandarin }}
%
\createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive, \skillsix}
%
\section{Projects}
\begin{multicols}{2} % Start a two-column layout
\noindent % Prevents indentation of the first line in each column
\datedexperience{kodekloud-downloader}{April 2023}
\explanation{Download Manager for KodeKloud}{\href{https://github.com/debakarr/kodekloud-downloader}{\faGithub\ \footnotesize Source}}
\explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Developed a download manager for KodeKloud with features for downloading video lessons and quizzes.
}

\datedexperience{kisskh-dl}{July 2022}
\explanation{CDrama/KDrama Downloader}{\href{https://github.com/debakarr/kisskh-dl}{\faGithub\ \footnotesize Source}}
\explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Created a command-line tool for downloading and decrypting shows from kisskh.co.
}

\columnbreak % This command forces the following content into the next column

\datedexperience{Flappy NEAT}{February 2018}
\explanation{NeuroEvolution Game}{\href{https://github.com/debakarr/Flappy-Bird-using-NeuroEvolution-of-Augmenting-Topologies/}{\faGithub\ \footnotesize Source}} 
\explanationdetail{
    \smallskip
    \coloredbullet\ %
    Implemented a Flappy Bird game using the NeuroEvolution of Augmenting Topologies algorithm.
}

\datedexperience{Myanimelist Data Set Creator}{February 2018}
\explanation{Anime Data Parser}{\href{https://github.com/debakarr/myanimelist-data-set-creator/}{\faGithub\ \footnotesize Source}}
\explanationdetail{
    \smallskip
    \coloredbullet\ %
    Created a tool for parsing and storing myanimelist.net data.
}
\end{multicols} % End the two-column layout
%
\section{Open Source Contributions}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Contributed to various open source projects, enhancing functionality and fixing bugs. My contributions can be viewed on my GitHub profile: \href{https://github.com/debakarr}{https://github.com/debakarr}.
	\smallskip
}
%
\end{document}
